04_DESeq_sexes

### 2019-12-23 analysis/04_LDA.Rmd
now with new lda analysis

knitr::opts_chunk$set(fig.path = '../figures/sexes/', cache = TRUE,  message=F, comment=FALSE, warning=FALSE)
```

@@

a <- ggplot(LDA.pit, aes(x = LD1, LD2, color = predictedstage)) + geom_point(shape = 17) + theme(legend.position = "none") + scale_color_manual(values = colorscharmaip)
b <- ggplot(LDA.pit, aes(x = LD1, LD2, color = treatment)) + geom_point(shape = 17) + theme(legend.position = "none") + scale_color_manual(values = colorscharmaip)

@@

a <- ggplot(LDA.gon, aes(x = LD1, LD2, color = predictedstage)) + geom_point(shape = 15) + theme(legend.position = "none") + scale_color_manual(values = colorscharmaip)
b <- ggplot(LDA.gon, aes(x = LD1, LD2, color = treatment)) + geom_point(shape = 15) + theme(legend.position = "none") + scale_color_manual(values = colorscharmaip)

@@

LDA.gon %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n())

```

>>>>

knitr::opts_chunk$set(fig.path = '../figures/LDA/', cache = TRUE,  message=F, comment=FALSE, warning=FALSE)
```

@@

c <- ggplot(LDA.pit, aes(x = LD1, LD2, color = predictedstage)) + geom_point(shape = 17) + theme(legend.position = "none") + scale_color_manual(values = colorscharmaip)
d <- ggplot(LDA.pit, aes(x = LD1, LD2, color = treatment)) + geom_point(shape = 17) + theme(legend.position = "none") + scale_color_manual(values = colorscharmaip)

@@

e <- ggplot(LDA.gon, aes(x = LD1, LD2, color = predictedstage)) + geom_point(shape = 15) + theme(legend.position = "none") + scale_color_manual(values = colorscharmaip)
f <- ggplot(LDA.gon, aes(x = LD1, LD2, color = treatment)) + geom_point(shape = 15) + theme(legend.position = "none") + scale_color_manual(values = colorscharmaip)

plot_grid(a,b,c,d,e,f, nrow = 3)

@@

LDA.gon %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n())
```
